A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-17 paper/paper.Rnw
fix sexpr issues

Receiver Operating Characteristic (ROC) curves are a type diagnostic plot which compare the false positive rate to the true positive rate for a classification method, and the Area Under the Curve (AUC) \svp{is a summary measure which} quantifies the \svp{overall accuracy of the model}. %It doesn't really summarize the shape - you can have very different shapes of curves with the same AUC value.
Perfect prediction would be indicated by a right angle along the upper left corner of the plot, with a corresponding AUC of 1, and a diagonal line with an AUC of 0.5 would indicate that the classification method performs no better than random chance. \autoref{fig:overall-roc} shows the ROC curve for \fix{the model} across all classes, and \autoref{fig:class-roc} shows the curve for each class. The full model has an AUC of 0.88, and the AUC for individual classes ranges from 0.81 (for lines) to 0.91 (for bowtie and text). \fix{pull these numbers out of the model using \\Sexpr} While the class performances do vary slightly, each ROC curve is the same general shape and performs significantly better than random chance. The points in \autoref{fig:class-roc} represent the equal error rate (EER), which is the threshold where there is equal probability of a false positive or false negative error. We will use the class-wise EER to set a threshold corresponding to each class, so that any model prediction with probability above the EER for that shape is considered a positive prediction.

>>>>

Receiver Operating Characteristic (ROC) curves are a type diagnostic plot which compare the false positive rate to the true positive rate for a classification method, and the Area Under the Curve (AUC) \svp{is a summary measure which} quantifies the \svp{overall accuracy of the model}. %It doesn't really summarize the shape - you can have very different shapes of curves with the same AUC value.
Perfect prediction would be indicated by a right angle along the upper left corner of the plot, with a corresponding AUC of 1, and a diagonal line with an AUC of 0.5 would indicate that the classification method performs no better than random chance. \autoref{fig:overall-roc} shows the ROC curve for \fix{the model} across all classes, and \autoref{fig:class-roc} shows the curve for each class. The full model has an AUC of 0.88, and the AUC for individual classes ranges from 0.81 (for lines) to 0.91 (for bowtie and text). \fix{pull these numbers out of the model using Sexpr} While the class performances do vary slightly, each ROC curve is the same general shape and performs significantly better than random chance. The points in \autoref{fig:class-roc} represent the equal error rate (EER), which is the threshold where there is equal probability of a false positive or false negative error. We will use the class-wise EER to set a threshold corresponding to each class, so that any model prediction with probability above the EER for that shape is considered a positive prediction.
